Binary companions of red giant stars with APOGEE I: \\ catalog and companions that survive the common envelope

### 2017-12-01 paper/1-catalog/twoface-catalog.tex

% to-do list
% ----------
% - write a first draft of the introduction
% - list our assumptions for detection & characterization (TheJoker)

@@

% adjust AAS-TEX shit
\setlength{\parindent}{1.1\baselineskip}

% define macros for text
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\sdssiii}{\project{\acronym{SDSS-III}}}
\newcommand{\thejoker}{\project{The~Joker}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\DR}{\acronym{DR13}}
\newcommand{\RC}{\acronym{RC}}
\newcommand{\RGB}{\acronym{RGB}}

@@

\title{Binary companions of red giant stars I: \\
       catalog and companions that survive the common envelope}

@@

\author{Jason~Cao}
\affiliation{Center for Cosmology and Particle Physics,
             Department of Physics,
             New York University, 726 Broadway,
             New York, NY 10003, USA}

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to find stellar,
sub-stellar, and planetary companions.
The \apogee\ survey (\DR) has measured multi-epoch but sparse radial velocities
for $> XX$ (mainly red giant) stars.
Though even few observations are useful for detecting companions, such data are
difficult to use for constraining the physical properties of companions because
permitted orbital solutions are highly degenerate.
% Aims
Here we perform a search for secondary companions of \nRC\ red clump (\RC) and
\nRGB\ red giant branch (\RGB) stars that have similar radii to \RC\ stars
using data from the \apogee\ survey.
Because the primary-star masses are known, the mass-function degeneracy is
broken and the secondary-companion masses ($m\,\sin i$) can be inferred.
% Methods
We use a custom-built Monte Carlo sampler (\thejoker) combined with prior
measurements of primary masses and stellar parameters to deliver (often highly
multi-modal) posterior beliefs about companion mass, pericenter distance, and
other orbital parameters for the \RC\ and \RGB\ stars.
% Results
We deliver a catalog of \ncompanions\ companions \todo{that meet some criteria},
and posterior samplings for all \ntotal\ stars in the parent sample.
We find \todo{describe} differences between the companions around \RC\ and \RGB\
stars that are \todo{in/consistent} with the theoretical prediction that
stellar companions should not survive the common-envelope \RGB\ phase.
We additionally find trends with chemical abundances, and we find tentative
evidence for ZZZ and WWW.
\end{abstract}

@@

\subsection{Re-measured radial velocities}\label{sec:rv-remeasure}

@@

\subsection{A catalog of red-clump binary systems} \label{sec:rc-catalog}

@@

>>>>

% to-do list
% ----------
% - write a first draft of the introduction
% - list our assumptions for detection & characterization (TheJoker)
% - Check abstract numbers (~80,000 RG stars with 3 or more good visits?)

@@

% adjust AAS-TEX shit
% \setlength{\parindent}{1.1\baselineskip}

% define macros for text
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\sdssiii}{\project{\acronym{SDSS-III}}}
\newcommand{\thejoker}{\project{The~Joker}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\DR}{\acronym{DR14}}
\newcommand{\RC}{\acronym{RC}}
\newcommand{\RGB}{\acronym{RGB}}

@@

\title{Binary companions of red giant stars with APOGEE I: \\
       catalog and companions that survive the common envelope}

@@

% \author{Jason~Cao}
% \affiliation{Center for Cosmology and Particle Physics,
%              Department of Physics,
%              New York University, 726 Broadway,
%              New York, NY 10003, USA}

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar-,
sub-stellar, and planetary-mass companions.
Even few observations are useful for detecting companions, though such data are
difficult to use for constraining the physical properties of companions because
permitted orbital solutions are highly degenerate.
% Aims
Here we perform a search for secondary companions of red giant branch (\RGB)
stars using data from the \apogee\ survey (\DR), which has measured multi-epoch
($\geq 3$) but sparse radial velocities for $> 80,000$ \RGB\ stars.
In some cases, where the primary-star masses are known, the mass-function
degeneracy is broken and the secondary-companion masses ($m_2\,\sin i$) can be
inferred.
% Methods
We use a custom-built Monte Carlo sampler (\thejoker) combined with stellar
parameters and primary mass estimates to deliver (often highly multi-modal)
posterior beliefs about companion mass, pericenter distance, and other orbital
parameters for the stars.
We compare the companion populations of red clump (\RC) versus \RGB\ stars at
similar surface gravity and temperature, and study the metallicity dependence
of companion properties.
% Results
We provide a catalog of \ncompanions\ companions for which the companion
properties can be confidently determined, along with posterior samplings for all
\ntotal\ stars in the parent sample.
\todo{We find differences between the companions around \RC\ and \RGB\
stars that are in/consistent with the theoretical prediction that
stellar companions should not survive the common-envelope \RGB\ phase.}
\todo{We additionally find trends in XX with chemical abundances.}

\end{abstract}

@@

@@

\subsection{A catalog of confident companions} \label{sec:conf-companions}

@@

\subsection{Trends in RGB companions with chemical abundances}
\label{sec:rgb-chemistry}
